---
title: "Activity 5 - Mini-competition Explorations"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

Loading the data
```{r}
# Load the data from the URL
url <- "https://raw.githubusercontent.com/chdl17/activity-05-mini-competition/main/competition-files/data/allendale-students.csv"
allendale_students <- read.csv(url)

# View the data
head(allendale_students)
```

Non-linearity of the data:
```{r}
plot(Final_Grade ~ Hours_Studied, data = allendale_students)

```

The plot shows a positive linear relationship between the variables, indicating that the assumption of linearity may hold.


Correlation of error terms
```{r}
model <- lm(Final_Grade ~ Hours_Studied, data = allendale_students)
plot(model$fitted.values, model$residuals)
```

The plot shows no pattern, indicating that the assumption of uncorrelated errors may hold.


Non-constant variance of error terms
```{r}
# Create a scale-location plot
plot(model$fitted.values, abs(model$residuals))
```

The plot shows that the spread of the residuals is roughly equal across all values of the predicted variable, indicating that the assumption of constant variance may hold.

Outliers
```{r}
# Create a boxplot of the residuals
plot(Hours_Studied, model$residuals)
```

The plot shows no outliers, indicating that there may be no outliers in the data.

